Renal IV

### 2017-07-03 msk1.rmd
Finished reading, added to be completed

>>>>

## Principles of fracture Mx

### Initial

Maintain/improve:

-  Blood supply
-  Soft tissue health

Open fractures

-  Prevent infn: antibiotics immediately
-  Allow fracture to heal
-  Restore fn in the limb

### Non-operative therapy

-  Casting: contraindicated if = {no displacement, displacement exists but not relevant to fn outcome, reduction impossible, reduction cannot be maintained, fracture produced by traction forces}
-  Traction = {skin, skeletal}

### Surgical therapy

-  Kirschner wires
-  Plates = {buttress, compression, neutralisation, tension-band, bridge} and screws
-  External fixation: used with open fractures that have significant soft tissue disruption
